---
title: "ex-2"
author: "Vignesh"
date: "24 September 2023"
output: html_document
---


```{r include=FALSE}
library(tidyverse)
```


1. What’s gone wrong with this code? Why are the points not blue?

```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, color = "blue"))
```

**Solution:**
  - 
  

2. Which variables in mpg are categorical? Which variables are continuous? (Hint: type ?mpg to read the documentation for the dataset). How can you see this information when you run mpg?

**Solution:**
  
```{r}
```


3. Map a continuous variable to color, size, and shape. How do these aesthetics behave differently for categorical vs. continuous variables?

**Solution:**

```{r}

```


4. What happens if you map the same variable to multiple aesthetics?

```{r}

```


5. What does the stroke aesthetic do? What shapes does it work with? (Hint: use ?geom_point)

```{r}
?geom_point
```

```{r}
ggplot(mtcars, aes(wt, mpg)) +
  geom_point(shape = 21, color = "black", fill = "white", size = 5, stroke = 5)
```


6. What happens if you map an aesthetic to something other than a variable name, like aes(colour = displ < 5)?

```{r}

```

